### 2018-05-06 papers/synth/experiments.tex
updated table

    plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\in0.224fty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & add: 1 edge bit, 1 node bit, del: 1 E, 1 AE, 1 AN\\\hline
    plos2-dia[4C] & 0.266 & 0   & 0.3229 & 0  & 1.409  & 0 & 2.114 & 0 &  0.3378 & 0 \\\hline
    mukund[3/4C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
    node4[-]  & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
    yeast-graph[3C]   & 95.0162    & 1 edge   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:qf-graph}
\end{table}

>>>>

    plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\in0.224fty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & add: 1 edge bit, 1 node bit, del: 1 E, 1 AE, 1 AN\\\hline
    plos2-dia[4C] & 0.266 & 0   & 0.3229 & 0  & 1.409  & 0 & 2.114 & 0 &  0.3378 & 0 \\\hline
    mukund[3/4C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
    node4[-]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
    yeast-graph[3C]   & 95.0162    & 1 E   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:qf-graph}
\end{table}
